---
title: "Sigmagraph: network visualization using Sigma.js v2.4.0"
author: "Thomas Charlon"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Sigmagraph enables to visualize networks using the latest stable version of Sigma.js. Graphs are created using the igraph package.

## Visualization overview

This package uses ggplot-like grammar: a basic visualization is first created and then modified by adding/removing attributes with additional functions, using the pipe operator from the magrittr package.  

The basic visualization is created with the sigma_from_igraph function, then various functions are called to control the aesthetics of the visualization, which all take a sigmagraph object as the first argument.

## Example

The dataset "Les Miserables" is included as a classic R graph example, which shows the co-appearances of the characters in the novel "Les Miserables".

```{r}
devtools::load_all()
library(sigmagraph)
library(igraph)

data(lesMis)
class(lesMis)
names(vertex_attr(lesMis))
names(edge_attr(lesMis))
```

Each node has an ID and a label, and each edge has a value equal to the number of co-appearances two characters had.  
To create a basic sigmagraph object, we call sigma_from_igraph:

```{r}
sig <- sigma_from_igraph(lesMis)
sig
```

We can resize the nodes using a fixed value:

```{r}
sig %>% add_node_size(one_size = 7)
```

Or using a node attribute:

```{r}
df_nodes = cbind.data.frame(name = vertex_attr(lesMis, 'id'),
  degree = degree(lesMis))

# seems sigma.js is not scaling automatically with min_size and max_size
# do it manually for now
df_nodes$degree %<>% scale(center = FALSE) %>% `*`(3) %>% `+`(3)

igraph = add_igraph_info(lesMis, df_nodes)

sig <- sigma_from_igraph(lesMis) %>%
 add_node_size(size_vector = vertex_attr(igraph, 'degree'), min_size = 3, max_size = 8)
sig
```

We can use the label attribute to change the node names displayed:

```{r}
sig %>%
  add_node_labels(label_attr = 'label')
```
